Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-12 preliminaries.tex
Add thm # from Mahadev QFHE

\begin{theorem} [from \cite{mahadev_qfhe}]
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine,
	there exists a classical-friendly quantum homomorphic encryption scheme.
\end{theorem}

>>>>

\begin{theorem} [Theorem 1.1 in \cite{mahadev_qfhe}]
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine,
	there exists a classical-friendly quantum homomorphic encryption scheme.
\end{theorem}
